final_project_draft

### 2022-03-28 draft.Rmd
March 28 graded before class commit. Made a few visualizations.

---
title: "final_project"
output: html_document
---

@@

## Political Donations
```{r}
library(tidyverse)
library(ggthemes)
pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
pol_donations <- pol_donations %>% rename(year = 'Election Year')
```

```{r}
pol_donations 
nfl <- pol_donations %>% filter(League == "NFL") 
nfl %>% group_by(Party) %>%
  summarise(n = n())
```

```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(desc(n))) %>%
  filter(rank <= 25) %>%
  mutate(owner = fct_reorder(.f = Owner, .x = n))

ggplot(data = owner_rank, aes(x = owner, y = n)) +
  geom_point(size=5, color="red", fill=alpha("orange", 0.3), alpha=0.7, shape=21, stroke=2) +
  geom_segment(aes(x = owner, xend = owner, y = 0, yend = n)) +
  coord_flip() +
    labs(title = "Most Frequent Donators Among All Leagues",
       y = "Count",
       x = "Owners") +
  theme_fivethirtyeight() 
```

## Blockbusters
```{r}
library(tidyverse)
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters

ggplot(data = blockbusters, aes(x = release_year, y = length_in_min)) +
  geom_line()
```

## History of Rock
```{r}
library(tidyverse)
history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")

history_of_rock %>%

led <- history_of_rock %>% filter(artist == "Led Zeppelin")

ggplot(data = led, aes(x = release_date, y = popularity)) +
  geom_line() 
```

## Unemployment

```{r}
unemployment_data_us <- read_csv("data/unemployment_data_us.csv")
unemployment_data_us
```

>>>>

---
title: "final_project_draft"
output: html_document
---

@@

## Political Donations of Professional Sports Team Owners 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(ggthemes)
pol_donations <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/sports-political-donations.csv")
pol_donations <- pol_donations %>% rename(year = 'Election Year') %>% mutate(amount = parse_number(Amount)) 
library(plotly)
```

## Owners Who Donate The Most Frequently and How Much 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

frequent <- pol_donations %>% group_by(Owner) %>%
    mutate(n = n()) %>%
    filter(n >= 65) %>%
  arrange(n) %>%
  mutate(donations = as.numeric(n)) %>%
  mutate(order = fct_reorder(.f = Owner, .x = donations))

plot1 <- ggplot(data = frequent, aes(x = amount, y = order, label = Amount, colour = League)) +
  geom_point() +
  labs(title = "Owners Who Have Made the Most Donations",
       y = "Owners",
       x = "Amount Donated",
       colour = "League") +
  theme_fivethirtyeight() +
  scale_colour_brewer(palette = "Dark2")

ggplotly(plot1, tooltip = "label") 
```

## Top 25 Highest Political Donations by NFL Team Owners in 2016 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
high_donations <- pol_donations %>% filter(year == "2016" & League == "NFL") %>%
  mutate(amount = parse_number(Amount)) %>%
  arrange(desc(amount)) %>%
  mutate(Rank = rank(desc(amount))) %>%
  filter(Rank <= 25) %>%
  mutate(owner_ordered = fct_reorder(.f = Owner, .x = amount)) %>%
  mutate(party = fct_relevel(Party, c("Republican", "Democrat", "Bipartisan")))

plot2 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = "Amount Donated",
       y = "Owner",
       title = "Top 25 Highest Political Donations by NFL Team Owners in 2016",
       colour = "Political Party",
       subtitle = "What Influence May Wealthy Elites Have on National Elections?") +
  theme_fivethirtyeight()  +
  scale_colour_manual(values = c("red", "blue", "yellow"))

ggplotly(plot2, tooltip = "label") 
```

## Blockbusters
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(ggrepel)
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters
```

## 5 Highest & Lowest IMBD Ratings Highlighted by Title
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters %>% group_by(mpaa_rating) %>%
  summarise(n = n())

blockbusters1 <- blockbusters %>% filter(!is.na(mpaa_rating))

interest <- blockbusters1 %>% mutate(rank = rank(desc(imdb_rating))) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5)

interest2 <- blockbusters1 %>% mutate(rank = rank(imdb_rating)) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5)

ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating)) +
  geom_point() +
  geom_label_repel(data = interest, aes(label = film_title), show.legend = FALSE) +
  geom_label_repel(data = interest2, aes(label = film_title), show.legend = FALSE) +
   geom_point(data = interest, size = 3, shape = 1, show.legend = FALSE) +
   geom_point(data = interest2, size = 3, shape = 1, show.legend = FALSE) +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019",
       subtitle = "5 Highest & Lowest IMBD Ratings Highlighted by Title") +
  theme_fivethirtyeight() +
  scale_colour_brewer(palette = "Dark2")
```

## History of Rock
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")
history_of_rock
```

## Most Popular Nirvana Songs 
```{r}
history_of_rock %>% group_by(artist) %>%
  summarise(n = n()) %>% arrange(desc(n))

nirvana <- history_of_rock %>% filter(artist == "Nirvana") %>% arrange(desc(popularity)) %>%
  mutate(order = fct_reorder(.f = name, .x = popularity)) %>%
  rename(Release_Date = 'release_date')
nirvana %>% select(order, everything())

plot3 <- ggplot(data = nirvana, aes(x = popularity, y = order, label = Release_Date)) +
  geom_point() +
  geom_segment(aes(x = popularity, xend = popularity, y = 0, yend = order)) +
  coord_flip() +
  labs(x = "Popularity",
       y = "Song Title",
       title = "Most Popular Nirvana Songs")

ggplotly(plot3, tooltip = "label")
```

## Unemployment
```{r}
unemployment_data_us <- read_csv("data/unemployment_data_us.csv")
unemployment_data_us
```
